---
title: "Inspect-DataFinal"
author: "Matt Pettis"
date: "June 21, 2019"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
```

# Load Data

I will usually put `load_*()` functions in a `lib-load.R` file and source that
file in all of my Rmd files so I have a single point of truth about how to load
and pre-process a file.  Here, for brevity, I'll define the load function and
use it.

```{r}
# This has no error handling at this point, but it does define the column types so that
# read_csv() doesn't have to guess at types.
# I will also eventually include any preprocessing that I want always done in this function.
load_finalData <- function() {
    read_csv(here("dat", "FinalData.csv"), col_types = "iciccccddddcccccc")
}
```

Now load the data:
```{r}
df_orig <- load_finalData()
```

# Inspect the data

I like to use the `{inspectdf}` package to look for ranges and missing values in
a table.  It's a very nice, compact, and intuitive display.


## Display a few lines

Often nice to just look at a sample of the data
```{r}
df_orig %>%
    print()
```

But there are prettier html tables too.  See the following link:

https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

```{r}
df_orig %>%
    knitr::kable()
```


## Missing Data

```{r}
inspectdf::inspect_na(df_orig, show_plot = TRUE)
```

## Categorical Data

Let's see what the breakdown of the categorical data looks like.

Note that in the plot, the gray boxes represent missing data.
```{r}
inspectdf::inspect_cat(df_orig, show_plot = TRUE)
```


## Numeric Data

This has been a hit-or-miss chart for me, depending on how many numerical values
I have.  I usually have to be more hands-on in making plots of a numeric type to
highlight what I want.

```{r}
inspectdf::inspect_num(df_orig, show_plot = TRUE)
```
